### 2021-03-15 paper.Rmd
add Laa transformation figure

XXX I would like Fig 5 of @Laa2020-uv as an illustration here

> figure 7 diagram of burning sage transformation

>>>>

\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/laa_radial_transformation.pdf}
\caption{An illustration of the radial transformation. Each panel represents linear projections of $p$ dimensional equidistant circles. As $p$ increases the circles get pushed further to the edge.}
\label{fig:tour-transformation}
\end{figure*}
